---
title: "p8105_hw1_bac2214"
author: "Brianna Carnagie"
date: "2023-09-15"
output: github_document
---

```{r, message = FALSE }
library(moderndive)
```

# Problem 1 
This code chunk loads the data set:

```{r}
data("early_january_weather")
```

This code chunk creates values for the questions asked in problem 1: 
```{r variablef for weather table}
num_rows = nrow(early_january_weather)
num_col = ncol(early_january_weather)

variable_contents = ls(early_january_weather)

print(variable_contents)

mean_temperature = mean(early_january_weather$temp)
mean_temperature_rounded = round(mean_temperature, digits = 2)
```

After running this code chunk, I see that the `r data("early_january_weather")` dataset contains **`r num_col`** columns and **`r num_rows`** rows. The dataset contains basic information in regards to weather for the first `r max(early_january_weather$day)` days in January including but not limited to the humidity, temperature, and wind speed every hour. According to this dataset, the first 15 days in January had an average temperature of `r mean_temperature_rounded` degrees Fahrenheit.


This code chunk will create the scatterplot.

```{r,echo = FALSE} 
library(ggplot2)
```


```{r}
question1_plot = ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()

print(question1_plot)
```

This code exports the project directory to my project directory.
```{r saving plot, message=FALSE}
ggsave("question1_plot.png", plot = question1_plot)
```


The plot seems to zig zag up and down from left to right (which I expect correlates to a higher temperature during the daylight and a lower temperature during the night time), but I notice a gradual increase in temperature as the month of January progresses.The lowest temperature is just below 25 degrees while the highest temperature is slightly above 55 degrees.

```{r library loag, echo = FALSE, message = FALSE}
library(tidyverse)
```






# Problem 2
This code chunk creates the data frame: 
```{r df_create}

hw_df <- tibble(
  rsamp = rnorm(10),
  log_vec = rsamp > 0,
  char_vec = c("apple", "banana", "cherry", "watermelon", "pineapple", "grape", "kiwi", "blueberry", "mango", "orange"),
  factor_vec = factor(
    rep(c("mild", "medium", "spicy"), length.out = 10),
    levels = c("mild", "medium", "spicy")
  )
)
```


Taking the means here:

```{r}
mean_rsamp <- hw_df %>% pull(rsamp) %>% mean()
mean_log_vec <- hw_df %>% pull(log_vec) %>% mean()
mean_char_vec <- hw_df %>% pull(char_vec) %>% mean()
mean_factor_vec <- hw_df %>% pull(factor_vec) %>% mean()

```

When pulling the means for the 4 different types of variables in hw_df, I was able to get a mean of `r format(round(mean_rsamp, 2))` for the random samples and `r format(round(mean_log_vec, 2))` for the logical vector. However, I got a warning message when trying to take the mean of the chracter vector and factor vector.

