---
title: "p8105_hw1_bac2214"
author: "Brianna Carnagie"
date: "2023-09-15"
output: github_document
---

```{r, message = FALSE }
library(moderndive)
```

# Problem 1 
This code chunk loads the data set:

```{r}
data("early_january_weather")
```

This code chunk creates values for the questions asked in problem 1: 
```{r}
num_rows = nrow(early_january_weather)
num_col = ncol(early_january_weather)

variable_contents = ls(early_january_weather)

print(variable_contents)

mean_temperature = mean(early_january_weather$temp)
mean_temperature_rounded = round(mean_temperature, digits = 2)
```

After running this code chunk, I see that the `r data("early_january_weather")` dataset contains **`r num_col`** columns and **`r num_rows`** rows. The dataset contains basic information in regards to weather for the first `r max(early_january_weather$day)` days in January including but not limited to the humidity, temperature, and wind speed every hour. According to this dataset, the first 15 days in January had an average temperature of `r mean_temperature_rounded` degrees Fahrenheit.


This code chunk will create the scatterplot.

```{r,echo = FALSE} 
library(ggplot2)
```


```{r}
question1_plot = ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()

print(question1_plot)
```

This code exports the project directory to my project directory.
```{r, message=FALSE}
ggsave("question1_plot.png", plot = question1_plot)
```


The plot seems to zig zag up and down from left to right (which I expect correlates to a higher tempature during the daylinght and a lower temprature during the night time), but I notice a gradual increase in temperature as the month of January progresses.The lowest temperature is just below 25 degrees while the highest temperature is slightly above 55 degrees.


